Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-19 article-models-ttdp.tex
small improvs

\subsection{Dependent products are taken fiberwise}
The rules explaining that substitution is compatible with the dependent product
constructor assert that dependent products are taken fiberwise (as is usual).

@@

\subsubsection{Dependent products are compatible with the identity functions}?

>>>>

\subsubsection{Dependent products are taken fiberwise}
The rules explaining that substitution is compatible with the dependent product
constructor assert that dependent products are taken fiberwise (as is usual).

@@

\subsubsection{Dependent products are compatible with the identity functions}
